QPLIB: A Library of Quadratic Programming Instances

### 2017-01-28 QPLIB-3.tex
revise/update section on website

\subsection{Website}
%Select subset or categories of instances (EXTRACT FROM THE LIBRARY A SUBSET OF INSTANCES WITH SPECIFIC CHARACTERISTICS)
%\todo[inline]{TASK X : write }

The instances of QPLIB are publically accessible at the website \url{http://qplib.zib.de}.
%
Beyond links to the \texttt{gms} and \texttt{lp} format files, the website provides a rich set of metadata for each
instance: the three letter problem classification (as described in Section \ref{subsec:final set}), basic properties such as the number of variables and constraints of
different types, the sense and curvature of the objective function, and information on the nonzero structure of the
problem.
%
In addition, we display a visualization of the sparsity patterns of the Jacobian and the Hessian matrix of the
Lagrangian function.  In the plots of the Jacobian nonzero pattern, the linear and nonlinear entries are distinguished
by color.  Figure... shows an example for instance QPLIB...

The entire set of instances can be explored in a searchable and sortable table of selected instance features: problem
classification, convexity of the continuous relaxation, and number of variables, constraints, and nonzeros.
%
Finally, a statistics page displays diagrams on the composition of the library according to different criteria: the
number instances according to problem type, variable types, convexity, number of variables and constraints, and density.
%
A table containing the relevant metadata for each instance can be downloaded in \texttt{csv} format and as spreadsheets
such that researchers can easily compile their own subset of instances according to these statistics.

>>>>

\subsection{Website}
%Select subset or categories of instances (EXTRACT FROM THE LIBRARY A SUBSET OF INSTANCES WITH SPECIFIC CHARACTERISTICS)

The instances of QPLIB are publicly accessible at the website \url{http://qplib.zib.de}.
%
Beyond all instances in GAMS and \texttt{.lp} format, the website provides a rich set of metadata for each
instance: the three letter problem classification (as described in Section \ref{subsec:final set}), basic properties such as the number of variables and constraints of
different types, the sense and convexity/concavity of the objective function, and information on the nonzero structure of the
problem.
%
In addition, we display a visualization of the sparsity patterns of the Jacobian and the Hessian matrix of the
Lagrangian function.  In the plots of the Jacobian nonzero pattern, the linear and nonlinear entries are distinguished
by color.  Figure... shows an example for instance QPLIB... \todo{add figure}

The entire set of instances can be explored in a searchable and sortable table of selected instance features: problem
classification, convexity of the continuous relaxation, number of (all, binary, integer) variables, (all, quadratic) constraints, nonzeros, hard eigenvalues in $Q^0$, and density of $Q^0$.
%
Finally, a statistics page displays diagrams on the composition of the library according to different criteria: the
number instances according to problem type, variable and constraint types, convexity, number of variables and constraints, and density.
%
A file containing the relevant metadata for each instance can be downloaded in comma-separated-values (\texttt{csv}) format,
so that researchers can easily compile their own subset of instances according to these statistics.
